Update of the ozone dry deposition in the OsloCTM3 v1.0

### 2018-10-08 DryDep.tex
Removed some parts of the abstract, e.g., reference to EMEP. Needs more work at some point.

\begin{abstract}
  Since the industrial revolution, tropospheric background ozone concentrations have been increasing strongly mainly in the northern hemisphere. In recent years, the number of episodes of peak concentrations especially in summertime has been decreasing in North America and Europe due to the implementation of air quality regulations. At the same time, fast developing countries, like e.g., China or India, saw a significant increase in ozone related air pollution. High concentrations of ozone in ambient air are hazardous not only to humans but to the ecosystem in general. The impact of ozone damage on vegetation and agricultural plants in particular may even affect food security in the future. Most chemistry-transport models (CTMs) and chemistry-climate models (CCMs) tend to overestimate surface ozone values. This may be partly due to uncertainties in the distribution and amount of precursor species and stratosphere-troposphere exchange as well as scavenging processes removing ozone from the atmosphere. Removal of any gas through gravitational settling or by uptake by plants and soil is referred to as dry deposition. The process of dry deposition is important for predicting surface ozone concentrations and understanding the observed amount and increase of tropospheric background ozone. Dry deposition velocities are typically calculated following a resistance-analogous approach wherein aerodynamic, quasi laminar, and canopy resistances are key components, but these conceptual dry deposition velocities are hard to measure explicitly. Following the European Monitoring and Evaluation Programme (EMEP) MSC-W chemistry transport model, we compute canopy resistance from stomatal conductance. In this paper, we present an update on the dry deposition scheme implemented in the OsloCTM3v1.0 and evaluate the model with respect to ozone and different parameters in the stomatal conductance parameterization, e.g., photosynthetic photon flux density (PPFD) and phenology. Furthermore, we investigate the impact on modeled ozone concentrations, both at the surface and in the free troposphere. We show that ozone dry deposition in the new version (v.1.1) decreases with respect to the previous version (v1.0), leading to an increase in surface ozone of up to ??\,\unit{\%}. We also put our results in context to recent multi-model studies as well as satellite data. {\bf TODO: Finsish the results section as soon as there are results.}
\end{abstract}

>>>>

\begin{abstract}
  Since the industrial revolution, tropospheric background ozone concentrations have been increasing strongly mainly in the northern hemisphere. In recent years, the number of episodes of peak concentrations especially in summertime has been decreasing in North America and Europe due to the implementation of air quality regulations. At the same time, fast developing countries, like e.g., China or India, saw a significant increase in ozone related air pollution. High concentrations of ozone in ambient air are hazardous not only to humans but to the ecosystem in general. The impact of ozone damage on vegetation and agricultural plants in particular may even affect food security in the future. Most chemistry-transport models (CTMs) and chemistry-climate models (CCMs) tend to overestimate surface ozone values. This may be partly due to uncertainties in the distribution and amount of precursor species and stratosphere-troposphere exchange as well as scavenging processes removing ozone from the atmosphere. Removal of any gas through gravitational settling or by uptake by plants and soil is referred to as dry deposition. The process of dry deposition is important for predicting surface ozone concentrations and understanding the observed amount and increase of tropospheric background ozone. Dry deposition velocities are typically calculated following a resistance-analogous approach wherein aerodynamic, quasi laminar, and canopy resistances are key components, but these conceptual dry deposition velocities are hard to measure explicitly. In this paper, we present an update on the general dry deposition scheme implemented in the OsloCTM3v1.0. We evaluate the resulting modelled ozone dry deposition with respect to obervations and multi-model studies. We will also estimate the impact of a set of parameters on the modeled ozone concentrations, both at the surface and in the free troposphere. We show that ozone dry deposition decreases with respect to the previous version, leading to an increase in surface ozone of up to ??\,\unit{\%}. {\bf TODO: Finsish the results section as soon as there are results.}
\end{abstract}
